---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rflashtext

<!-- badges: start -->
[![R-CMD-check](https://github.com/AbrJA/rflashtext/workflows/R-CMD-check/badge.svg)](https://github.com/AbrJA/rflashtext/actions)
[![Grand-total](https://cranlogs.r-pkg.org/badges/grand-total/rflashtext)](https://cran.r-project.org/web/packages/rflashtext/index.html)
[![Per-month](https://cranlogs.r-pkg.org/badges/rflashtext)](https://cran.r-project.org/web/packages/rflashtext/index.html)
<!-- badges: end -->

_rflashtext_ **can be used to find and replace words in a given text with only one pass over the document.** 

It's a R implementation of the [FlashText algorithm](https://arxiv.org/abs/1711.00046) and it's inspired on the python library [flashtext](https://github.com/vi3k6i5/flashtext).

## Installation

You can install the released version of rflashtext from [CRAN](https://cran.r-project.org/web/packages/rflashtext/index.html) with:

``` r
install.packages("rflashtext")
```

And the development version from [GitHub](https://github.com/AbrJA/rflashtext) with:

``` r
# install.packages("devtools")
devtools::install_github("AbrJA/rflashtext")
```
## Example

This is a basic example which shows you how to use the API:

### New processor

```{r new}
devtools::install_github("AbrJA/rflashtext@rcpp")

library(rflashtext)

processor <- KeywordProcessor$new(keys = c("NY", "LA"), words = c("New York", "Los Angeles"))
processor$show_trie()
```

### Add keys-words to processor

```{r add}
processor$add_keys_words(keys = c("TX", "CA"), words = c("Texas", "California"))
processor$show_trie()
```

### Find keys in a sentence

```{r}
words_found <- processor$find_keys(sentences = c("I live in LA and I like NY", "Have you been in TX?"))
words_found
data.table::rbindlist(words_found)
```

### Replace keys in a sentence

```{r}
processor$replace_keys(sentences = c("I live in LA and I like NY", "Have you been in TX?"))
```

To see more details about the performance of the algorithm, click [here](https://github.com/AbrJA/rflashtext_benchmark.git).
